---
title: "Get Data"
output: html_notebook
---

# getSymbols

An unified interface to obtain data from multiple sources. 

```{r}
library(quantmod)
apple <- getSymbols(Symbols = "AAPL", src = "yahoo", auto.assign = FALSE)
head(apple)
```

The objects can be auto assigned to the environment.

```{r}
getSymbols("QQQ", src = "google")
getSymbols("SPY")
getSymbols("GDP", src = "FRED")
```

```{r}
autoplot.zoo(merge.xts(apple$AAPL.Adjusted, SPY$SPY.Close), facets = NULL)
```

# Quandl

Another option is to download the data from the Internet via the Quandl API.

```{r}
gdp <- Quandl("FRED/GDP", type = "xts")
autoplot.zoo(gdp)
```

 
##

```{r}
getSymbols("^BVSP")
autoplot.zoo(BVSP$BVSP.Close)
```

## From OHLC to what you need

The Quantmod package has the necessary tools to extract the columns you need. Starting with the initials in uppercase:

```{r}
autoplot.zoo(cbind(Cl(BVSP), Hi(BVSP)), facets = NULL) # Close and High
```

With tick data you can use getPrice:

```{r}
autoplot(getPrice(apple))
```

